Psychological Needs During Intergroup Contact

### 2022-01-17 Methods-and-Results.Rmd
order fix

@@

<!-- \input{Tables/descrFullLong} -->
<!-- \input{Tables/descrOutLong} -->

<!-- \input{Tables/mdlContactGeneral} -->
<!-- \input{Tables/mdlTheory} -->
<!-- \input{Tables/mdlRobustness} -->

<!-- \begin{figure}[h] -->

<!-- \centering -->

<!-- \caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.} -->

<!-- \makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}} -->

<!-- \label{fig:PrismaCombined} -->

<!-- \end{figure} -->

<!-- \input{Tables/ExclusionsCombined} -->

<!-- \input{Tables/TheoreticalExclusion} -->

<!-- \begin{figure}[h] -->

<!-- \centering -->

<!-- \caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature. (B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature. (C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].} -->

<!-- \includegraphics[width=\textwidth]{Figures/LiteratureComparison-1} -->

<!-- \caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.} -->

<!-- \label{fig:LiteratureComparison} -->

<!-- \end{figure} -->

>>>>

<!-- FIGURES: -->

@@
